Co-moving stars in \textsl{Gaia DR1}: a catalog of genuine comoving star pairs from low-resolution spectroscopic follow-up

### 2017-06-05 paper/comoving-followup.tex
fix table

To derive radial velocities for each source, we then measure the (wavelength)
line centroid of \Ha\ in each corrected spectrum.
We model the absorption line using a pixel-convolved Voigt profile and again use
a Gaussian process for the background model (with the same parameterizations as
described above).
We now use \lbfgsb\ optimization and the resulting maximum-likelihood parameters
to initialize a Markov Chain Monte Carlo (MCMC) sampling of the posterior
probability distribution over the 6 parameters: $\ln |A|$, $x_0$, $\ln\sigma_G$,
$\ln\gamma_L$, $\ln\sigma_{3/2}$, and $\ln\rho_{3/2}$.
The linear amplitude, $A$, is assumed to be negative (i.e. \Ha\ is assumed to be
an absorption feature) and is computed from the corresponding parameter as $A =
-\exp(\ln |A|)$.
We use uniform priors on all parameters except $\ln\rho_{3/2}$, for which we use
a Gaussian; prior parameters are specified in \tablename~\ref{tbl:prior-bounds}.
\todo{Explain MCMC, emcee, steps, etc.}
\figurename~\ref{fig:Halpha-mcmc} shows \todo{mcmc shite}.
With the resulting posterior samples, we compute the median and median absolute
deviation (MAD) of the marginal distribution over line centroid, $x_0$.
We use the MAD to estimate the standard deviation ($\sigma \approx 1.5~{\rm
MAD}$, assuming the samples are Gaussian distributed) of the samples and find
that the typical velocity \emph{precision} from measuring the centroid of \Ha\ is between $2$--$10~\kms$ \todo{double check numbers}.

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{ c | c }
      \toprule
        Parameter & Prior \\\toprule
        $\ln A$ & $\mathcal{U}(2, 16)$\\
        $x_0$ & $\mathcal{U}(\lambda_{\Ha}-16, \lambda_{\Ha}+16)$ [${\rm \AA}$]\\
        $\ln\sigma_G$ & $\mathcal{U}(-8, 2)$ [${\rm \AA}$]\\
        $\ln\gamma_L$ & $\mathcal{U}(-8, 2)$ [${\rm \AA}$]\\
        $\ln\sigma_{3/2}$ & $\mathcal{U}(-8, 8)$\\
        $\ln\rho_{3/2}$ & $\mathcal{N}(1, 1)$ [${\rm \AA}$]\\
      \bottomrule
    \end{tabular}
    \caption{
      Priors used for \Ha\ line profile model parameters.
      $\mathcal{U}(a, b)$ indicates a uniform prior between $a$ and $b$ and
      $\mathcal{N}(\mu, \sigma^2)$ indicates a normal distribution with mean
      $\mu$ and variance $\sigma^2$.
      $\lambda_{\Ha}$ is the true \Ha\ line centroid in angstroms.
      \label{tbl:prior-bounds}
    }
  \end{center}
\end{table}

>>>>

To derive radial velocities for each source, we then measure the (wavelength)
line centroid of \Ha\ in each corrected spectrum.
We model the absorption line using a pixel-convolved Voigt profile and again use
a Gaussian process for the background model (with the same parameterizations as
described above).
We now use \lbfgsb\ optimization and the resulting maximum-likelihood parameters
to initialize a Markov Chain Monte Carlo (MCMC) sampling of the posterior
probability distribution over the 6 parameters: $\ln |A|$, $x_0$, $\ln\sigma_G$,
$\ln\gamma_L$, $\ln\sigma_{3/2}$, and $\ln\rho_{3/2}$.
The linear amplitude, $A$, is assumed to be negative (i.e. \Ha\ is assumed to be
an absorption feature) and is computed from the corresponding parameter as $A =
-\exp(\ln |A|)$.
We use uniform priors on all parameters except $\ln\rho_{3/2}$, for which we use
a Gaussian; prior parameters are specified in \tablename~\ref{tbl:prior-bounds}.
\todo{Explain MCMC, emcee, steps, etc.}
\figurename~\ref{fig:Halpha-mcmc} shows \todo{mcmc shite}.
With the resulting posterior samples, we compute the median and median absolute
deviation (MAD) of the marginal distribution over line centroid, $x_0$.
We use the MAD to estimate the standard deviation ($\sigma \approx 1.5\times{\rm
MAD}$, assuming the samples are Gaussian distributed) of the samples and find
that the typical velocity \emph{precision} from measuring the centroid of \Ha\ is between $2$--$10~\kms$ \todo{double check numbers}.

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{ c | c }
      \toprule
        Parameter & Prior \\\toprule
        $\ln A$ & $\mathcal{U}(2, 16)$\\
        $x_0$ & $\mathcal{U}(6547, 6579)$\\
        $\ln\sigma_G$ & $\mathcal{U}(-8, 2)$\\
        $\ln\gamma_L$ & $\mathcal{U}(-8, 2)$\\
        $\ln\sigma_{3/2}$ & $\mathcal{U}(-8, 8)$\\
        $\ln\rho_{3/2}$ & $\mathcal{N}(1, 1)$\\
      \bottomrule
    \end{tabular}
    \caption{
      Priors used for \Ha\ line profile model parameters.
      $\mathcal{U}(a, b)$ indicates a uniform prior between $a$ and $b$ and
      $\mathcal{N}(\mu, \sigma^2)$ indicates a normal distribution with mean
      $\mu$ and variance $\sigma^2$.
      Wavelength units are all angstroms.
      \label{tbl:prior-bounds}
    }
  \end{center}
\end{table}
